### 2015-05-07 evaluation.tex
updates to evaluation

\begin{table*}[t]
\small
\centering
\caption{Runtime comparison with different yield instrumentation granularities and context-switch bounds.}
\label{tab:results}
\begin{tabular}{l rrr rrr rr r r}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\end{table*}

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 8 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities (see Section~\ref{whoop:bugfinding}): \yieldcoarse and \yieldmr.

>>>>

\begin{table*}[t]
\small
\centering
\setlength{\tabcolsep}{0.5em}
\caption{Comparison with different yield instrumentation granularities and context-switch bounds.}
\label{tab:results}
\begin{tabular}{l r rrrr rrrr rrrr}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\end{table*}

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 8 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{whoop:bugfinding}), and also uses all the optimisations discussed in Section~\ref{whoop:optimizations}.
